---
title: "snRNAseq GE downstream analyses report"
author: "Darren Cameron"
date: "`r format(Sys.time(), '%d/%m/%y')`"
output: 
  html_document:
    theme: paper
---

MAGMA, sLDSR, scDRS results for Shi et al (2021) data

*** 

### **Results** {.tabset}

#### **Sub-clusters** {.tabset}

```{r Subclusters, fig.dim = c(15, 10), echo = FALSE, results="asis"}
for(REGION in c('MGE', 'LGE', 'CGE', 'Progenitor')) {
  cat("  \n##### **", REGION , "**\n", sep = "")
  cat("\n***\n", sep = "")
  plot(get(paste0('shi_', REGION, '_group_plot_0.5')))
  cat("\n\n***\n", sep = "")
  plot(get(paste0('shi_', REGION, '_lvl2_umap_0.5')))
  cat("\n\n***\n", sep = "")
  plot(get(paste0('shi_', REGION, '_cluster_stats_0.5')))
  cat("\n\n***\n", sep = "")
  cat("  \n")
}
```


#### **Cell counts** {.tabset}

```{r Cell counts, fig.dim = c(5, 5), echo = FALSE, results="asis"}
for(LEVEL in c('lvl1', 'lvl2')) {
  cat("  \n##### **", LEVEL, "**\n", sep = "")
  cat("\n***\n", sep = "")
  print(knitr::kable(get(paste0('cnts_', LEVEL)), format = "html", table.attr = "style='width:30%;'"))
  cat("\n\n***\n", sep = "")
  cat("  \n")
}
```

#### **MAGMA** {.tabset}

```{r Magma, fig.dim = c(15, 10), echo = FALSE, results="asis"}
for(REGION in c('lvl1', 'lvl2', 'cond_lvl2', 'cond_lvl2_internal')) {
  cat("  \n##### **", REGION, "**\n", sep = "")
  cat("\nMAGMA: 35UP_10_DOWN\n\nLDSR: 100UP_100DOWN\n")
  cat("\n***\n", sep = "")
  plot(get(paste0('magma_ldsr_', REGION,'_plot')))
  cat("\n\n***\n", sep = "")
  cat("  \n")
}
```

#### **Cell IDs** {.tabset}

**Suggested encoding**:

+ MGE - Str-Ctx-InNs - Striatal and cortical interneurons
+ MGE - SubP-Chol-InNs - Subpallial cholinergic neurons
+ MGE - Ctx-InNs - Cortical interneurons

+ LGE - OB-N - Olfactory Bulb neuron precursor
+ LGE - D1-MSN-A - D1 MSN (PDYN) precursor
+ LGE - D1-MSN-B - D1 MSN (TSHZ1) precursor
+ LGE - D2-MSN - D2 MSN precursor

***

```{r Cell IDs, fig.dim = c(5, 5), echo = FALSE, results="asis"}
print(knitr::kable(lvl2_cell_types, format = "html", table.attr = "style='width:30%;'"))
cat("\n\n***\n", sep = "")
cat("  \n")
```

#### **MAGMA downsample** {.tabset}

```{r Magma_downsample, fig.dim = c(15, 10), echo = FALSE, results="asis"}
for(LEVEL in c('lvl1', 'lvl2')) {
  cat("  \n##### **", LEVEL, "**\n", sep = "")
  cat("\nLevel 1: Downsampled to 254 cells (number of MG cells)\n\nLevel: - Downsampled to 300 cells (28 of 30 cells)\n")
  cat("\n\n***\n", sep = "")
  plot(get(paste0('magma_dnwSmple_scatter_', LEVEL, '_plot')))
  cat("\n\n***\n", sep = "")
  plot(get(paste0('magma_dwnSmple_', LEVEL, '_plot')))
  cat("\n\n*** \n", sep = "")
  cat("  \n")
}
```

#### **LDSR downsample** {.tabset}

```{r LDSR_downsample, fig.dim = c(15, 10), echo = FALSE, results="asis"}
for(LEVEL in c('lvl1', 'lvl2')) {
  cat("  \n##### **", LEVEL, "**\n", sep = "")
  cat("\nLevel 1: Downsampled to 254 cells (number of MG cells)\n\nLevel: - Downsampled to 300 cells (28 of 30 cells)\n")
  cat("\n\n***\n", sep = "")
  plot(get(paste0('ldsr_dnwSmple_scatter_', LEVEL, '_plot')))
  cat("\n\n***\n", sep = "")
  #plot(get(paste0('ldsr_dwnSmple_', LEVEL, '_plot')))
  cat("\n\n*** \n", sep = "")
  cat("  \n")
}
```

#### **Gene Windows** {.tabset}

```{r Gene_windows, fig.dim = c(15, 10), echo = FALSE, results="asis"}
for(WINDOW in c('magma_windows', 'ldsr_windows')) {
  cat("  \n##### **", WINDOW , "**\n", sep = "")
  cat("\n\n***\n", sep = "")
  plot(get(paste0(WINDOW, '_lvl1_plot')))
  cat("\n\n*** \n", sep = "")
  cat("  \n")
}
```

#### **scDRS** {.tabset}

```{r scDRS, fig.dim = c(15, 10), echo = FALSE, results="asis", warning=FALSE}
for(REGION in c('all', 'MGE', 'LGE', 'CGE', 'Progenitor')) {
  cat("  \n##### **", REGION , "**\n", sep = "")
  cat("\n\n***\n", sep = "")
  plot(get(paste0('scDRS_', REGION, '_umap')))
  cat("\n\n***\n", sep = "")
  cat("SCZ group heatmap")
  cat("\nNote: Table reports raw values, heatmap show FDR corrected values\n\nSquare: Sig group GWAS assoc.\n\nCross: Sig hetero GWAS assoc.")
  plot(get(paste0('scDRS_', REGION, '_group_heatmap')))
  cat("\n\n***\n", sep = "")
  cat("SCZ group table results")
  print(knitr::kable(get(paste0('scDRS_', REGION, '_SCZ_group'))))
  cat("\n\n***\n", sep = "")
  cat("HEIGHT group table results")
  print(knitr::kable(get(paste0('scDRS_', REGION, '_HEIGHT_group'))))
  cat("\n\n*** \n", sep = "")
  cat("  \n")
}
```

